\documentclass[a4paper,10pt]{article}
%-----------------------------------------------------------
\usepackage[top=0.75in, bottom=0.75in, left=0.55in, right=0.85in]{geometry}
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\usepackage{palatino}
\usepackage{tabularx}
\fontfamily{SansSerif}

\selectfont

\usepackage[T1]{fontenc}
\usepackage
%[ansinew]
[utf8]
{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\isep}{-2 pt}
\newcommand{\lsep}{-0.5cm}
\newcommand{\psep}{-0.6cm}
\renewcommand{\labelitemii}{$\circ$}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{6.62in}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
% \hspace{0.5cm}\\[-0.2cm]

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\Large SHUBHAM JAROLI} \\
\textbf{R.No 205, BH-1,
ABV-IIITM, Morena Link Road, 
Gwalior (M.P.)- 474015}\\
\textbf{shubham15.jaroli@gmail.com} |
\textbf{+91-8889857636} \\
% \indent Alt Mob No.: \textbf{1234567890} \\
\end{tabular*}

\resheading{\textbf{ACADEMIC DETAILS} }\\[\lsep]
\\ \\
%\begin{table}[ht!]
%\begin{center}
\indent \begin{tabular}{ l @{\hskip 0.30in} l @{\hskip 0.30in} l @{\hskip 0.30in} l @{\hskip 0.35in} l }
\hline
\textbf{Qualification} & \textbf{Institute/Board} & \textbf{Year} & \textbf{CGPA/\%} \\
\hline
Integrated Post Graduation (B.Tech  \,\, & ABV-Indian Institute of Information & 2019* & 8.22/10.0 \\
+M.Tech) in Information Technology & Technology and Management, Gwalior \\
Higher Secondary Examination & Central Academy Senior Secondary & 2013 & 92.60\\
& School, Udaipur (CBSE) &  \\
Secondary Examination & Central Academy Senior Secondary & 2011 & 10.0/10.0\\
& School, Udaipur (CBSE) &  \\
\hline
\end{tabular}
\indent *Expected year of graduation, CGPA till 6th semester.
%\end{center}
%\end{table}
\\ 

\resheading{\textbf{AREAS OF INTEREST} }\\[\lsep]
\begin{itemize}
\item \indent \textbf{Data Analysis, Web Development, Data Structures and Algorithms.}
\end{itemize}

\resheading{\textbf{TECHNICAL SKILLS} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Data Structures and Algorithms} 
\end{itemize}
\begin{itemize}
\item \noindent \textbf{Programming Languages-}  C, C++, Python
\end{itemize}
\begin{itemize}
\item \noindent\textbf{ Operating Systems-}  Linux, Windows
\end{itemize}
\begin{itemize}
\item \noindent \textbf{ Web Scripting languages- }  HTML, CSS, JavaScript
\end{itemize}
\begin{itemize}
\item \noindent\textbf{ Web Frameworks-}  Django, Bootstrap, JQuery, JSON, AJAX
\end{itemize}
\begin{itemize}
\item \noindent\textbf{ Databases-}  MySQL, MondoDB
\end{itemize}
\begin{itemize}
\item \noindent\textbf{ Tools-}  Git, \LaTeX, NumPy, Pandas, Adobe Photoshop, Anaconda, C++ STL
\end{itemize}

\resheading{\textbf{PROJECTS } }\\[\lsep]
\begin{itemize}
\item \textbf{Hospital Readmission Prediction of Diabetic Patients using Deep Neural Networks
} (B.Tech Thesis Project) \\
 \emph \textbf{(May-July 2017)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	
	\item Worked extensively to build a Recurrent Neural Network (RNN) model to predict the hospital readmission possibilities of diabetic patients on non sequential data. 
    \item Compared accuracy given by RNN model with classic models like Support Vector Machine , Random Forest and two-layer simple neural network model.
    \item \textbf{Tools:-} Python, Scikit-Learn, Tensorflow.

	\end{itemize}

\item \textbf{One-4-All
} (Start-Up Project)  \\
 \emph \textbf{(January-March 2017)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item Two way event management website which acts as an interface between consumers and providers.
	\item \textbf {Tools:-} Python/Django, REST API, Bootstrap, Java Script.
	\end{itemize}
\end{itemize}


\begin{itemize}
\item \textbf{shorten-it
}  (Self-Learning Project)\\
 \emph \textbf{(December 2016)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item A URL shortening service based on the concept of Bitly.com which shortens any long URL or link to randomly generated string. 
	\item\textbf {Tools:-} Python/Django, Bootstrap, Java Script.
	\end{itemize}
\end{itemize}

\begin{itemize}
\item \textbf{Let-Us-Blog
}  (Self-Learning Project)\\
 \emph \textbf{(October-November 2016)} \\[-0.6cm]
	\begin{itemize}\itemsep \isep
	\item A blogging website having commenting, liking, log-in and image uploading facilities. 
	\item\textbf {Tools:-} Python/Django, Bootstrap, Java Script, Crispy Forms.
	\end{itemize}
\end{itemize}

\resheading{\textbf{EXPERIENCES AND POSITIONS OF RESPONSIBILITY }}\\[\lsep]
\begin{itemize}
\item \textbf{Core team member of Abhigayan Abhikaushlam Students’ Forum (AASF) at IIIT, Gwalior }
\begin{itemize}\itemsep \isep
	\item Worked as hIQ coordinator as well as technical head. My responsibilities included conducting both technical events (tutorial Sessions on various technical topics and programming contests) and managerial events. 
	\end{itemize}
\end{itemize}

\begin{itemize}
\item \textbf{Vice-President of Social Welfare Club- Rotaract Club of Youth (RCoY) at IIIT, Gwalior }
\begin{itemize}\itemsep \isep
	\item Organized various cloth donation camps, weekly educational program for poor people and children of nearby slums and orphanage named \textbf{Shanti-Niketan}.
	\end{itemize}
\end{itemize}

\begin{itemize}
\item \textbf{Head of Event Management Team in National Level Techo-Managerial Fest INFOTSAV'16 held at IIIT Gwalior }
\end{itemize}


\resheading{\textbf{PUBLICATIONS AND ACHIEVEMENTS }}\\[\lsep]
\begin{itemize}
\item \textbf{Research Paper entitled} \textit{"RECURRENT NEURAL NETWORK WITH NON SEQUENTIAL DATA TO PREDICT HOSPITAL READMISSION OF DIABETIC PATIENTS"}\textbf{ accepted at International Conference on Computational Biology and Bio-informatics (ICCBB) 2017 at New Jersey, USA and to be published in ACM digital library.}
\end{itemize}
\begin{itemize}
\item \textbf{1st Prize in Case-Study Contest and Brand-Aid Competition organized by students' forum, AASF. }
\end{itemize}


\resheading{\textbf{EXTRA CURRICULAR ACTIVITIES} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{Content editor and designer of annual magazine of institute: ABHISHAR.}
\item \noindent \textbf{Member of Organizing Committee of Institute Industry Interaction (III)'17 conducted to facilitate communication between the industry and academia at IIIT, Gwalior.}
\item \noindent \textbf{Student Volunteer of Corna, Rock-Band Competition in Annual Cultural Fest of institute: AURORA-2K15.} 
\item \noindent \textbf{Organized Blood Donation Camp at institute.}
\item \noindent \textbf{Took part in various literary and oratory events like GD, JAM, Case Study contests, BIT quiz organized by students' forum, AASF.}
\end{itemize}

\resheading{\textbf{PROFILE LINK} }\\[\lsep]
\begin{itemize}
\item \noindent \textbf{LinkedIn:}\href{https://www.linkedin.com/in/shubham-jaroli-47302bb6}{ https://www.linkedin.com/in/shubham-jaroli-47302bb6}

\item \noindent \textbf{Github:}\href{https://github.com/19shubham}{ https://github.com/19shubham}

\end{itemize}



\end{document}

